\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{listings}

\geometry{margin=1in}
\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  urlcolor=blue!70!black,
  pdftitle={Tracklist Engine Alignment Program Plan},
  pdfauthor={Tracklist Engine}
}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  frame=single,
  rulecolor=\color{black!20},
  backgroundcolor=\color{black!3}
}

\title{Alignment Program Plan\\[0.4em]
  \large GT Export \textrightarrow{} Stem-Quality Cascade \textrightarrow{} MERT \textrightarrow{} Aligner}
\author{Tracklist Engine \quad|\quad set \texttt{1fsnxchk} (Big Bootie Vol.\ 12)}
\date{2026-06-05 --- canonical source: \texttt{alignment\_program\_plan.md}}

\begin{document}
\maketitle

\begin{abstract}
Shared cross-agent program plan for the alignment stage of Tracklist Engine.
\textbf{Canonical editable source: \texttt{alignment\_program\_plan.md}.}
Phase~1 exports BB12 Ableton ground truth into \texttt{set\_ground\_truth}; later phases
build stem quality via a priority cascade, upgrade separation to RoFormer ensembles,
backfill MERT embeddings, and prototype the span aligner $f_\theta(A,T,D)\to L$.
Companion docs: \texttt{alignment\_objective.md}, \texttt{stem\_discovery\_playbook.md},
\texttt{embedding\_backfill\_plan.md}.
\end{abstract}

\tableofcontents
\newpage

\section{Context}

Manual labeling of Big Bootie Vol.\ 12 (\texttt{set\_id = 1fsnxchk}) is complete in
Ableton (\path|~/Desktop/big bootie 12 labeling Project/big bootie 12 labeling_fast.als|;
re-parse on disk every run).

Two forces drive this program:
\begin{enumerate}[noitemsep]
  \item Extract human ground truth $L^*$ into \texttt{set\_ground\_truth} (deliverable~A).
  \item The quality ceiling of the pipeline is set by \textbf{stem source type}, not the
        separator---so stem acquisition is a \emph{priority cascade}, and MERT must be
        recomputed with correct sequencing (see \S\ref{sec:mert}).
\end{enumerate}

\noindent\textbf{DAG:}
\texttt{core $\cdot$ scrape $\to$ ingest $\to$ analysis $\to$ labeling $\to$ (GT) $\to$ alignment}.

\section{Formal Objective}\label{sec:formal}

Fold into \texttt{docs/alignment\_objective.md} (Phase~0).

\begin{equation}
  f_\theta(A,T,D) \to L
\end{equation}

\noindent Render invariant: $E_a(L)=\hat{A}$, $d(\hat{A},A)<\epsilon$; $L$ = minimum
information to reproduce the set within perceptual $\epsilon$.

\begin{itemize}[noitemsep]
  \item \textbf{Metric:} structured perceptual $d$, \emph{not} Frobenius
        $\|\hat{A}-A\|_F^2$. Pin $\epsilon$ via listening study; proxy later with
        \texttt{set\_playback\_score.reconstruction\_mfcc\_distance}. No numeric
        $\epsilon$ / waveform loss in v1 training.
  \item \textbf{MDL:}
        $L^*=\arg\min_L[\mathrm{bits}(L)+\lambda\,d(E_a(L),A)]$ --- rate term encodes
        importance: placement $\gg$ stem $\gg$ bpm/key $\gg$ FX/transitions.
  \item $T$ is a \textbf{constraint} (alignment over finite $D$, not open transcription).
  \item $E_a$ is non-differentiable $\Rightarrow$ render invariant = eval/reward; train
        supervised on $L^*$ first.
  \item \textbf{Degenerate cheat:} $E_a(L)$ can paste slices of $A$; rate term +
        placement-identity supervision block ``play $A$'' collapse.
  \item $L$ admits refs $\notin D$ via \texttt{ref\_source = mix\_extract} (and related).
  \item Stem \textbf{discovery} stays out of $f_\theta$; it is ingest (Phase~2).
\end{itemize}

\subsection{Tiered $L$}

\begin{center}
\begin{tabular}{@{}clll@{}}
\toprule
Tier & Content & Schema home & This program \\
\midrule
1 & Placement, spans, \texttt{ref\_segments}, \texttt{slot\_label} & \texttt{set\_ground\_truth} & P1 \\
2 & Stem select + \texttt{ref\_source} & \texttt{set\_ground\_truth} & P1 \\
3 & \texttt{tempo\_ratio} (span-level bpm) & GT DSL + DB & P1 \\
4 & \texttt{pitch\_shift\_semi} (span-level key) & GT DSL + DB & P1 \\
5 & FX, volume, transitions & deferred & later \\
play & Atomic measure grid $L_{\mathrm{play}}$ & \texttt{measure\_alignment} & P5+ \\
\bottomrule
\end{tabular}
\end{center}

\section{Phase Overview}

\begin{center}
\begin{tabular}{@{}cl@{}}
\toprule
Phase & Scope \\
\midrule
P0 & Formal objective $\to$ \texttt{alignment\_objective.md} \\
P1 & BB12 GT export + schema/write-back patches \\
P1.5 & Ingest BB12 placed stem winners into \texttt{track\_audio} \\
P2 & Stem-quality priority cascade (ingest) \\
P3 & RoFormer separation backend (ingest/analysis) \\
P4 & MERT backfill (analysis; split sequencing) \\
P5 & Span aligner prototype \\
\bottomrule
\end{tabular}
\end{center}

\section{Phase 1 --- BB12 GT Export}\label{sec:p1}

\textbf{Critical path;} depends on nothing else.

\begin{lstlisting}
.als -> export_als_to_gt.py -> bb12_ground_truth.yaml
     -> write_back_ground_truth.py -> set_ground_truth
\end{lstlisting}

\subsection{Session structure (verified)}

\begin{itemize}[noitemsep]
  \item Track~1: \texttt{1-mix} (set-time anchor).
  \item Track~2: \texttt{2-mix\_instrumental} (skip).
  \item 40 top-level GroupTracks = mashup sections (e.g.\ Honest $\times$ Mean).
  \item GT = every \textbf{kept} placed clip past track~2 (after clip hygiene).
  \item Mashup simultaneity: one YAML row per \emph{layer} (not one row per group).
\end{itemize}

\subsection{Identity (outsourced to aligning folder)}

Parse clip \textbf{SourceContext/OriginalFileRef/Path} (prefer over
\texttt{Samples/Imported} copy):

\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
Path shape & Slot & \texttt{claimed\_stem} \\
\midrule
\texttt{tracks/NNN[wK]\_\_\ldots} & \texttt{NNN[wK]} & \texttt{regular} \\
\texttt{stems/NNN\_\_\ldots/candidates/vocals/\ldots} & \texttt{NNN} & \texttt{acappella} \\
\texttt{stems/NNN\_\_\ldots/vocals.flac} (Demucs) & \texttt{NNN} & \texttt{acappella} \\
\texttt{stems/NNN\_\_\ldots/candidates/instrumental/\ldots} & \texttt{NNN} & \texttt{instrumental} \\
\texttt{stems/NNN\_\_\ldots/instrumental.flac} & \texttt{NNN} & \texttt{instrumental} \\
\bottomrule
\end{tabular}
\end{center}

Join \texttt{NNN[wK]} to \texttt{manifest.json} \texttt{local\_path} prefix
$\to$ \texttt{recording\_id}. Strip user tags \texttt{[NNNbpm KK]}. Legacy BB12
manifest lacks \texttt{label}/\texttt{version}/\texttt{stem} --- parse slot from path only.
Unresolved Rvmor \texttt{w}-rows $\to$ \texttt{recording\_id=null} + flag.

\subsection{Time mapping}

\begin{itemize}[noitemsep]
  \item \textbf{Set spans:} map arrangement beats through \texttt{1-mix} warp markers
        (\texttt{content\_beat = LoopStart + (arr - CurrentStart)} $\to$ SecTime).
        Interpolation primary; linear fallback if markers absent.
  \item \textbf{Ref spans:} clip warp markers + \texttt{Loop/LoopStart}.
  \item \textbf{Bpm:} \texttt{tempo\_ratio = ref\_span\_s / set\_span\_s}.
  \item \textbf{Key:} \texttt{pitch\_shift\_semi} from \texttt{PitchCoarse} (+ \texttt{PitchFine}).
\end{itemize}

\subsection{Parts played + clip hygiene (v1)}

\begin{enumerate}[noitemsep]
  \item \textbf{Parking-lot drop:} clips with \texttt{set\_start\_s > mix\_end\_s + tol}
        (mix ends ${\sim}$90:37; some refs have clips at 116--122\,min).
  \item \textbf{Abutting sliver merge:} sub-threshold clips glued to dominant neighbor
        (e.g.\ Maps 56:15--56:18) merge into dominant span.
  \item \textbf{Intentional loops:} comparable-size or overlapping clips on same track
        $\to$ \texttt{is\_loop: true} + \texttt{ref\_segments} per iteration.
  \item \textbf{Defer:} Blink-182 7-clip chop/stutter chain (effect vs.\ artifact);
        sub-clip jumps without separate arrangement regions (measure-level $L_{\mathrm{play}}$).
\end{enumerate}

Review table lists kept, dropped, and merged clips with reasons.
Optional \texttt{--include-all-clips} for debugging.

\subsection{Schema / write-back patches}

Add to \texttt{set\_ground\_truth}:
\begin{itemize}[noitemsep]
  \item \texttt{tempo\_ratio REAL}
  \item \texttt{pitch\_shift\_semi INTEGER}
  \item \texttt{ref\_source TEXT} --- \texttt{reference|official|phase\_cancel|
        online\_candidate|demucs|roformer|mix\_extract}
\end{itemize}

In \texttt{labeling/ground\_truth/schema.py}:
\texttt{slot\_label} (PK key, distinct from display title), plus fields above.

\texttt{write\_back\_ground\_truth.py}: use \texttt{slot\_label} as DB \texttt{label}
(fixes duplicate ``Honest'' title collisions).

\subsection{Verification (P1)}

Anchor-check 3--4 spans vs.\ Ableton playhead ($\pm{\sim}1$ beat); \texttt{schema.load} OK;
\texttt{write\_back --dry-run}; live write; confirm row count on pi-storage.

\section{Phase 1.5 --- BB12 Winner Ingest}

After export: batch-ingest placed \texttt{candidates/} and volcr.it winners via
\texttt{ingest\_stem\_url.py} so corpus $D$ matches $L^*$. Log source in
\texttt{track\_audio\_correction.reason}.

\section{Phase 2 --- Stem-Quality Priority Cascade}\label{sec:p2}

Reframe: source type dominates; separation is the floor; official/phase-derived is the ceiling.

\textbf{Discipline:} detect-then-correct, never blanket; log to \texttt{track\_audio\_correction};
version-aware matching via \texttt{core/identity.py}.

\subsection{2a --- Solvability (metadata)}

Discogs + MusicBrainz APIs: official instrumental/acappella exists?
Classify ${\sim}$18k tracks into tier~1 (official pair) / tier~2 (derive) / tier~3 (separation only).

\subsection{2b --- Tiered acquisition}

Lossless FLAC/WAV only (MP3 breaks phase-cancel):
stores/Stems packs $\to$ paid DJ pools (DJcity, BPM Supreme, ZIPDJ) $\to$
community (acapellas4u, voclr, YouTube; throttled, cached, ToS-aware).

\subsection{2c --- Derive + verify}

Reuse \path|~/aligning/phase-cancel/cancel.py| as-is:
official instrumental + full mix $\to$ acappella
(\texttt{adaptive --smooth 0.5 --fft 4096 --cap 4}).

\textbf{Sum-check:} aligned \texttt{acap + inst $\approx$ original} $\to$ residual score.

\subsection{2d --- Quality gate}

\begin{enumerate}[noitemsep]
  \item Identity/version: chromaprint + cross-correlation (chroma/low-mid); BPM/key prefilter.
  \item Sum-check residual (strongest when pair exists).
  \item Separator-as-judge bleed (RoFormer vocal on candidate instrumental).
  \item Watermark ASR lexicon (e.g.\ \texttt{digitalmusicpoolstudio.com}).
  \item Transcode detection (spectral cliff ${\sim}$16\,kHz).
  \item Coverage: vocal-activity vs RoFormer vocals (truncation).
\end{enumerate}

\textbf{Selection:} official pair $>$ phase-derived $>$ community beating separation floor $>$ separation.

\texttt{fetch\_candidate\_stems.py} stays labeling-support for audition; P2 cascade driver is separate.

\section{Phase 3 --- RoFormer Separation Backend}

Maximize SDR; cost not constrained. Replace Demucs floor with
\textbf{Mel-Band RoFormer + BS-RoFormer + SCNet-XL} ensemble (pluggable interface).

\begin{itemize}[noitemsep]
  \item \textbf{Vast (CUDA):} primary bulk path --- \texttt{audio-separator[gpu]} or MSST.
  \item \textbf{Mac (Apple Silicon):} use \texttt{ssmall256/mlx-audio-separator} --- stock
        MPS path silently falls back to CPU for unsupported ops.
  \item Validate SDR vs Demucs + bleed-judge ${\approx}0$ on known official instrumental before bulk.
  \item Re-separate existing Demucs \texttt{track\_stems} after validation.
\end{itemize}

\section{Phase 4 --- MERT Backfill}\label{sec:mert}

330M target: \textbf{0 tracks}; ${\sim}$4.5\% stale 95M (unmatchable). Clean full 330M recompute required.

\textbf{Split sequencing} (merged from program review):

\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
Task & When & Rationale \\
\midrule
6b set-side MERT & Parallel with P1 & Stem-independent; aligner prereq \\
6a regular refs & Parallel with P1 (BB12 + whitelist) & Wrong-audio excluded via 6d list \\
6c variant (acap/inst) & After P2 for those rows & Avoid embedding replaced audio \\
Re-embed changed rows & Incremental post-P2 & detect-then-correct \\
\bottomrule
\end{tabular}
\end{center}

Size disk/GPU-hours first (${\sim}$100+ GB at full corpus). Driver: \texttt{mert\_backfill\_loop.py} on Vast.

\section{Phase 5 --- Aligner Prototype}

\texttt{workspaces/} $\to$ promote to \texttt{alignment/}.

Supervised span aligner: inputs $A$ features + $T$ slots + $\{E(x)\}$; output span-level $L$
matching \texttt{GroundTruthTrack}.

Loss: Huber on spans; CE on \texttt{(recording\_id, claimed\_stem)}; set-multiplicity for mashups.

Later: distill to \texttt{measure\_alignment}; proxy $E_a$; listening study pins $\epsilon$.

\section{Critical Files}

\begin{itemize}[noitemsep]
  \item \textbf{New:} \texttt{labeling/export\_als\_to\_gt.py}; ingest solvability querier,
        cascade driver, sum-check, quality gate; RoFormer wrapper.
  \item \textbf{Edit:} \texttt{ground\_truth/schema.py}, \texttt{write\_back\_ground\_truth.py},
        \texttt{schema.sql}, \texttt{alignment\_objective.md}, playbooks.
  \item \textbf{Reuse:} \texttt{phase-cancel/cancel.py}, \texttt{fetch\_candidate\_stems.py},
        \texttt{ingest\_stem\_url.py}, \texttt{core/identity.py}, \texttt{mert\_backfill\_loop.py}.
  \item \textbf{Tests:} fixture \texttt{.als} for beat$\to$sec, path join, tempo/semi extraction.
\end{itemize}

\section{Risks}

\begin{itemize}[noitemsep]
  \item Live \texttt{.als} edits --- always re-parse.
  \item \texttt{pyexpat} broken in Py3.14 venv --- use \texttt{lxml} or \texttt{/usr/bin/python3}.
  \item Version disambiguation is the hard part of P2 --- wrong master breaks phase-cancel.
  \item Phase-cancel needs lossless, sample-accurate alignment.
  \item Don't blanket re-source/re-embed --- detect-then-correct.
  \item Community scraping: throttle/cache; personal-use copyright norms only.
\end{itemize}

\end{document}
